GNSS-based Displacement Detection Using Bayesian Inference for Deformation Monitoring

### 2021-09-03 paper/r1/manuscript-mssp.tex
r1 initial 参考文献 EKF

\usepackage{bm}
\usepackage{amsmath} 
\usepackage{amssymb}
\usepackage{float}
\usepackage{threeparttable}  
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{lipsum}
\usepackage{stfloats}
\usepackage{graphicx}      % insert graphic
\usepackage{subcaption}
\usepackage{lineno}
\linenumbers

@@

	%位移探测算法回顾，
	%传统位移探测的弊端
	%位移探测的短板1,关注与定位算法，忽略探测算法2，关注与longterm忽略shortterm
	%随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
	The first category is about the research of measurement technology in GNSS-based displacement detection.
	To evaluate the performance of single base station real time kinematic(RTK) and network real time kinematic(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}. The results showed that NRTK has advantages in accuracy and robustness.
	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}. The results showed that NRTK can achieve an accuracy of 4.7mm and 7.9mm in the horizontal and vertical directions respectively.
	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using precise point position(PPP) has been studied. The results showed that PPP can be capable of detecting large landslides.
	There are also some studies using the time-differenced carrier phases (TDCP) technique\cite{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection. This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
	In general, the above research mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.

	In another category of GNSS-based displacement detection research, GNSS is only used as a static positioning method.
	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data were used as a comparison. 
	The results showed that the accuracy of the Global positioning system (GPS) measurement over a period of 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
	The results of a nine-month of field monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
	In addition, GNSS was also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements were used as references\cite{atanasova2018ground,fuhrmann2015estimation}.
	In these studies, the GNSS static positioning mode is usually adopted.

@@

	\subsection{Relative Real-time Kinematic (RTK)}
	There are many real-time kinematic positioning models, among which RTK is the most widely used model in deformation monitoring.
	Kalman filter is used in the implementation of  RTK, and the observation model, the state model, and the extended Kalman filtering process of RTK are introduced below. 
	\subsubsection{Observation Model}
	The double-difference(DD) observation model is usually used in RTK, and its definition is as follows\cite{teunissen2017springer}.
	\begin{equation}
	\left. \begin{array}{l}
	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - \Delta \nabla I_{\Phi {i_{br}}}^{jk} + \Delta \nabla  T_{br}^{jk} + \Delta \nabla  M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla I_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla T_{br}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla  M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}
	\end{array} \right\}
	\label{eq_dd_obs}
	\end{equation}
	In this observation equation, $\Delta \nabla $ denotes the DD operator, $i$ denotes the frequency; $b$ and $r$ denote base station and rover station respectively; $j$ and $k$ represent the satellites;
	$\Delta \nabla P_{{{i}_{br}}}^{jk}$ and $\Delta \nabla \Phi _{{{i}_{br}}}^{jk}$ denote pseudo-range and carrier-phase DD observations, respectively; 
	$\Delta \nabla \rho _{br}^{jk}$ is the DD geometric distance between receivers and satellites; 
	$\Delta \nabla  M_{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla  M_{{{\Phi }_{{{i}_{br}}}}}^{jk}$ denote pseudo-range and carrier-phase multipath error, respectively; 
	$\Delta \nabla \varepsilon _{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \varepsilon _{{{\Phi }_{{{i}_{br}}}}}^{jk}$ represent DD measurement noise of pseudo-range and carrier-phase, respectively; 
	$\Delta \nabla  I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations\cite{teunissen2017springer}; $\Delta \nabla T_{br}^{jk}$is the DD tropospheric delay between receivers and satellites. 
	For the short baseline, the atmospheric error can be ignored, so the above DD observation equation is simplified as
	\begin{equation}
	\left. \begin{array}{l}
	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla  M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla  M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}\end{array} \right\}
	\label{eq_dd_obs_simplified}
	\end{equation}
	Ignoring the influence of multipath, the linearization form of formula (\ref{eq_dd_obs_simplified}) is expressed as
	\begin{equation}
	\label{eq_rtk_measure}
	{\bf{y}} = {\bf{Hx}} + {\bf{\varepsilon }}
	\end{equation}
	where $\bf{y}$ is the observation minus the computed,  $\bf{H} $ is the linearized design matrix\cite{hofmann-wellenhof2007gnss}, $\bf{x}\triangleq {{[{{\mathbf{r}}_{r}},\Delta \nabla \mathbf{N}]}^{T}}$, is the state vector, which contains the rover station coordinate ${{\mathbf{r}}_{r}}$ and the DD integer ambiguity $\Delta \nabla \mathbf{N}$;  $\mathbf{\varepsilon } $ is the observation noise, and its covariance matrix is expressed as  ${{\mathbf{R}}_{\varepsilon }} $.

	After forming the observation equation, the ‘float’ solution of the parameter can be obtained by the standard least square method. 
	The 'float' solution and variance of integer ambiguity are expressed as  $\Delta \nabla \mathbf{\tilde{N}} $,  ${{\mathbf{Q}}_{\Delta \nabla \mathbf{\tilde{N}}}} $, respectively. 
	To obtain high precision positioning results, it is necessary to fix the integer ambiguity. 
	The problem of ambiguity fixing can be described as\cite{teunissen1995the}.
	\begin{equation}
	\Delta \nabla {\bf{\hat N}} = \mathop {\arg min}\limits_{\Delta \nabla {\bf{N}} \in {\bf{Z}}} ((\Delta \nabla {\bf{N}} - \Delta  {\bf{\tilde N}}){\bf{Q}}_{\Delta \nabla {\bf{\tilde N}}}^{ - 1}{(\Delta \nabla {\bf{N}} - \Delta \nabla {\bf{\tilde N}})^T})
	\label{eq_lamda}
	\end{equation}
	There are many methods referring to integer ambiguity resolution, among which LAMBDA (Least-squares Ambiguity Decorrelation Adjustment)\cite{teunissen1995the} method is the most widely used one. The integer ambiguity is obtained by the integer least square method. Then, the test process is executed to determine whether to accept or reject the integer ambiguity\cite{teunissen2003integer,teunissen2005gnss}. If the test is passed, the fixed integer ambiguity can be substituted into (\ref{eq_rtk_measure}) to resolve the fixed solution, otherwise, the ‘float’ solution will be maintained.

	\subsubsection{State Model}
	The state model is defined as follows (Takasu 2013)
	\begin{equation}
	{{\bf{x}}_k} = {\bf{F}}{{\bf{x}}_{k - 1}} + {\bf{w}}
	\end{equation}
	where ${\bf{F}} \buildrel \Delta \over = \left[ {\begin{array}{*{20}{c}}
		{{{\bf{I}}_{3 \times 3}}}&{\bf{0}}\\
		{\bf{0}}&{{{\bf{I}}_{(2n - 2)(2n - 2)}}}
		\end{array}} \right]$ , is the transition matrix from $k-1$ to $k$; $\mathbf{I}$ denotes the identity matrix; $n$ represents the number of satellites observed simultaneously by the base station and the rover station; 
	Only GPS ${{L}_{1}}$ and ${{L}_{2}}$ frequency observations are considered, so $2n-2$ DD ambiguities are formed. 
	$\mathbf{w}$ is the process noise, and its covariance matrix is expressed as ${{\mathbf{G}}_{w}}$. 
	For kinematic positioning, the coordinate covariance component is set to be large to capture dynamic features, while the ambiguity covariance component is set to $\mathbf{0}$ to ensure the stability of positioning.
	\subsubsection{Extended Kalman filtering}
	Kalman filtering includes two processes: prediction update and measurement update\cite{grewal2001kalman}. The prediction process is as follows:
	\begin{equation}
	{{\bf{\hat x}}_{k|k - 1}} = {\bf{F}}{{\bf{\hat x}}_{k - 1}}
	\end{equation}
	\begin{equation}
	{{\bf{Q}}_{k|k - 1}} = {\bf{F}}{{\bf{Q}}_{k - 1}}{{\bf{F}}^T} + {{\bf{G}}_w}(k)
	\end{equation}
	where ${\bf{\hat x}}_{k|k - 1}$ is the predicted value and ${\bf{Q}}_{k|k - 1}$ is the corresponding covariance. According to the definition of the state transition matrix above, it can be seen that the state value of the previous epoch remains unchanged. However, the coordinate covariance component becomes larger, while the ambiguity covariance component remains unchanged. The measurement update process is as follows:
	\begin{equation}
	{{\bf{v}}_k} = {\bf{y}}(k) - {\bf{H}}_k{{\bf{\hat x}}_{k|k - 1}}
	\end{equation}
	\begin{equation}
	{{\bf{S}}_k} = {\bf{H}}_k{{\bf{Q}}_{k|k - 1}}{\bf{H}}{_k^{\rm{T}}} + {{\bf{R}}_\varepsilon }(k)
	\end{equation}
	\begin{equation}
	{\bf{K}} = {{\bf{Q}}_{k|k - 1}}{\bf{H}}_k^T{\bf{S}}_k^{ - 1}
	\end{equation}
	where ${{\mathbf{v}}_{k}}$ denotes the innovation vector, and ${{\mathbf{S}}_{k}}$ is the covariance matrix of the innovation vector; $\mathbf{K}$ is the state estimation gain matrix. The final state is estimated as follows:
	\begin{equation}
	{{\bf{\hat x}}_k} = {{\bf{\hat x}}_{k|k - 1}} + {\bf{K}}{{\bf{v}}_k}
	\end{equation}
	\begin{equation}
	{{\bf{Q}}_k} = {{\bf{Q}}_{k|k - 1}} - {\bf{K}}{{\bf{S}}_k}{{\bf{K}}^T}
	\end{equation}
	where ${{\mathbf{\hat{x}}}_{k}}$ is the final estimate, and ${{\mathbf{Q}}_{k}}$ is the corresponding covariance matrix; ${{\mathbf{\hat{x}}}_{k}}$ is the only input of the Bayesian inference.

	\subsection{Workflow of displacement detection }  
	In the previous paragraphs, the displacement detection model using Bayesian inference is proposed, and the principle of relative real-time kinematic positioning is presented.
	The workflow of the GNSS-based displacement detection using Bayesian inference is shown in Fig. \ref{fig_v_workflow}.
	\begin{figure*}[htpb]
		\centering
		\includegraphics[scale=0.45]{v_workflow}
		\caption{Bayesian model for displacement detection.}
		\label{fig_v_workflow}
	\end{figure*}

>>>>

\usepackage{bm}
\usepackage{amsmath} 
\usepackage{amssymb}
\usepackage{float}
\usepackage{threeparttable}  
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{lipsum}
\usepackage{stfloats}
\usepackage{graphicx}      % insert graphic
\usepackage{subcaption}
\usepackage{lineno}
\usepackage{color}
\definecolor{r_s}{RGB}{255,0,0}
\linenumbers

@@

	%位移探测算法回顾，
	%传统位移探测的弊端
	%位移探测的短板1,关注与定位算法，忽略探测算法2，关注与longterm忽略shortterm
	%随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
	The first category is about the research of measurement technology in GNSS-based displacement detection.
	To evaluate the performance of single base station real time kinematic(RTK) and network real time kinematic(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}. The results showed that NRTK has advantages in accuracy and robustness.
	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}. The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using precise point position(PPP) has been studied. The results showed that PPP can be capable of detecting large landslides.
	\textcolor{r_s}{
		Moschas et al.\cite{Moschas_2014} studied the extraction of strong motion displacement waveform by PPP and evaluated it through free vibration experiments. These results show that 10 Hz PPP-GPS is very useful for seismic engineering and can be safely used to reconstruct the deflection waveforms of various points on the ground and structure during strong motion.}
	\textcolor{r_s}{Zhang et al.\cite{Meng_2019} introduced Galileo augmenting GPS single-frequency single-epoch precise positioning method with baseline constrain for bridge dynamic monitoring, to improve the positioning availability and reliability, as well as narrow the search space, and increase the success rate of ambiguity resolution and positioning.
	Xue et al.\cite{Xue2021} comprehensively evaluated multi-GNSS low-cost receivers for deformation monitoring and concluded that the potential improvement of the precision of the low-cost receiver by using multi-GNSS measurements and a GNSS base station with a geodetic antenna.}
	There are also some studies using the time-differenced carrier phases (TDCP) technique\cite{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection. This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
	In general, the above research mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.

	\textcolor{r_s}{
	The other category is about displacement detection research based on GNSS.
	There are many studies on the use of high-rate GNSS for structure displacement extraction and parameter identification.
	Psimoulis et al.\cite{psimoulis2008_1,psimoulis2008_2} studied the feasibility of using GNSS for structural vibration detection. Experiments were carried out to evaluate the use of Global positioning system (GPS) to determine the parameters of oscillation of major structures.
	Meng et al.\cite{Meng_2018} presented the challenges faced by the design and implementation of a new monitoring system for large bridges. Damage detection in SHM of long-span bridges is very challenging because there is no general damage definition, and damage is usually unique and bridge-specific. Psimoulis et al.\cite{psimoulis2018detection} presented an algorithm named RT-SHAKE to detect ground motions, which aims to detect seismic motion more sensitively and robustly.	There are also studies on the relationship between receiver parameters and high-rate GNSS measurement\cite{Hberling2015,Moschas2015}.
	H{\"a}berling et al.\cite{Hberling2015} argued that due to the large error of dynamic GNSS measurement if high-rate GNSS is to be a valuable tool for seismic displacement measurement above 1 Hz, the baseband parameters of the GNSS receiver must be considered.
	Moschas et al.\cite{Moschas2015} studied the relationship between the phase-locked loop(PLL) bandwidth and noise in 100 Hz GPS measurement.
	The results show that the measurement correlation decreases with the increase of PLL bandwidth from low to high to 100 Hz. Shen et al.\cite{shennan_2019} gave a more detailed review of dynamic structural health monitoring technology based on GNSS. There are also studies on displacement detection such as landslide, and GNSS is usually used as a static positioning method.}
	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data were used as a comparison. 
	The results showed that the accuracy of the GPS measurement over a period of 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
	The results of a nine-month of field monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
	In addition, GNSS was also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements were used as references\cite{atanasova2018ground,fuhrmann2015estimation}.
	In these studies, the GNSS static positioning mode is usually adopted.

@@

	\subsection{Relative Real-time Kinematic (RTK)}
	There are many real-time kinematic positioning models, among which RTK is the most widely used model in deformation monitoring.
	\textcolor{r_s}{Therefore, in this work, RTK is adopted as the kinematic positioning model.
	RTK is implemented by extended Kalman filtering, where the design matrix is derived from the double-difference observation model, and the state transition matrix is the identity matrix.
For the covariance matrix of process noise, the coordinate covariance component is set to be large to capture dynamic features, while the ambiguity covariance component is set to $\mathbf{0}$ to ensure the stability of positioning\cite{takasu2011rtklib}.
}
	\subsection{Workflow of displacement detection }  
	In the previous paragraphs, the displacement detection model using Bayesian inference is proposed, and the \textcolor{r_s}{ kinematic positioning model is described.}
	The workflow of the GNSS-based displacement detection using Bayesian inference is shown in Fig. \ref{fig_v_workflow}.
	\begin{figure*}[htpb]
		\centering
		\includegraphics[scale=0.45]{v_workflow}
		\caption{Bayesian model for displacement detection.}
		\label{fig_v_workflow}
	\end{figure*}
